Hamby Data and `rtrees`

### 2020-09-29 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
removed cache and re-knit

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE, 
                      eval = TRUE,
                      cache = TRUE)
```

@@

When I look at the dimensions of my training data now and the number of predictions from `rtrees`, then agree now!

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  eval = TRUE,
  cache = FALSE
)
```

@@

When I look at the dimensions of my training data now and the number of predictions from `rtrees`, they agree now!
